---
title: "STAT416 Assignment 4"
author: "Ashish Jain"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = TRUE,
    message = FALSE,
    warning = FALSE
)
```
##Question 2:

####a).
```{r, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
p.values<-read.table("https://raw.githubusercontent.com/ashishjain1988/STAT416/master/HW4/hwk4_q2.txt")
p.value<-p.values[,1]
padjusta<-p.adjust(p.value,method = "bonferroni")
padjustTa<-rep(FALSE,length(padjusta))
padjustTa[padjusta<=0.05]<-TRUE
deg<-length(padjustTa[padjustTa == TRUE])
```

The number of differential expressed genes by using Bonferroni method are `r deg`.

####b).
```{r, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
padjust<-p.adjust(p.value,method = "holm")
padjustT<-rep(FALSE,length(padjust))
padjustT[padjust<=0.05]<-TRUE
deg<-length(padjustT[padjustT == TRUE])
```

The number of differential expressed genes by using Holm's method are `r deg`.

####c).
```{r, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
#c.
padjust<-p.adjust(p.value,method = "BH")
padjustT<-rep(FALSE,length(padjust))
padjustT[padjust<=0.05]<-TRUE
deg<-length(padjustT[padjustT == TRUE])
```

The number of differential expressed genes by using Benjamini and Hochberg’s method are `r deg`.

####d).
```{r, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
#source("http://bioconductor.org/biocLite.R")
#biocLite("qvalue")
library(qvalue)
qobj <- qvalue(p.value,fdr.level=0.05)
pi0Number<-qobj$pi0
STres <- qobj$qvalues
padjustTd<-rep(FALSE,length(STres))
padjustTd[STres<=0.05]<-TRUE
deg<-length(padjustTd[padjustTd == TRUE])
```

The number of differential expressed genes by using Storey and Tibshirani’s method are `r deg`. The $\pi_0$ value is `r pi0Number`.

####e).
```{r, tidy=TRUE, tidy.opts=list(width.cutoff=60)}
getTable<-function(padjust)
{
  first200<-padjust[1:200]
  TP<-length(first200[first200 == TRUE])
  FN<-200-TP
  other800<-padjust[201:1000]
  FP<-length(other800[other800 == TRUE])
  TN<-800-FP
  return(c(TN,FN,FP,TP))
}
parta<-getTable(padjustTa)
table<-data.frame(Properties=c("True Null","False Null"), "Accept Null"= c(parta[1],parta[2]),"Reject Null"=c(parta[3],parta[4]))
knitr::kable(table,caption = "Table for Part a")

parta<-getTable(padjustTd)
table<-data.frame(Properties=c("True Null","False Null"), "Accept Null"= c(parta[1],parta[2]),"Reject Null"=c(parta[3],parta[4]))
knitr::kable(table,caption = "Table for Part d")
```
